% !TEX root = memoria.tex
\documentclass[../../memoria.tex]{subfiles}

\begin{document}

\paragraph{}
Nowadays technology is present in practically any scenario, activity, business, situation, etc. Most of the work and productive activities of society have been modernized. Agriculture, which is one of the oldest activities of the human being has begun to be included in this transformation towards the digital world.

\paragraph{}
The inclusion of technology in agriculture facilitates a great number of tasks carried out on farmland, yet it is still a field with a long way to go. The rise of cloud computing and IoT devices has enabled new ways of applying technology to agriculture. This is how smart farming was born.

\paragraph{}
Thanks to smart farming, it is possible to control a cropland and perform actions on it in the most efficient way, which leads to a better development of this activity. This project proposes a way of acting and working, making use of different technologies and tools for this purpose that include the use of the public cloud, IoT devices and infrastructure as code in order to be able to develop a complete system that provides a solution for the need of monitoring a farmland. It has been developed thinking about both scalability and integration with other technologies and the total price of the deployed system.

\paragraph{}
This system will act as a base to establish a complete monitoring on variables such as atmospheric pressure, air temperature, air humidity, soil moisture, etc. that through its analysis will be possible to carry out automated actions on the crop fields, which will represent a great improvement in the efficiency of the today's agriculture.
\end{document}
